---
title: "ComputingTwoProject"
author: "Abigail McPheeters"
date: "4/16/2020"
output: html_document
---




Abi's Section 

My goal is to use a photoresistor (from the Elegoo Electronics Fun Kit) to record light and the time that elapses when there is light versus no light. This was to be used in a greenhuose to measure the amount of light in a day to compare with heat to see if tehre was a correlation with plant growth. However, the code is all I am able to work with in the current COVID-19 quarantine. 

```{Uno}
#light sensor code that runs on an Arduino
#this code does not run on Rstudio, but it runs on an Arduino Uno system
// /light sensor with LED to show when the change is registered
int LED = 13; //define LED digital pin 13
int val = 0; //define the voltage value of photo diode in digital pin 0
unsigned long timeLOW = 0; //will store last time LED was updated
void setup(){
 pinMode(LED,OUTPUT); // Configure LED as output mode
 Serial.begin(9600); //Configure baud rate 9600
}
void loop(){
 val = analogRead(0); // Read voltage value ranging from 0 -1023
 Serial.println(val); // read voltage value from serial monitor
 if(val<1000){ // If lower than 1000, turn off LED
 digitalWrite(LED,LOW);
 }else{ // Otherwise turn on LED
 digitalWrite(LED,HIGH);
}
 delay(10); // delay for 10ms;
 if (val<1000 == true){   //record time when daylight presence is detected
 timeLOW = millis();
 Serial.println("Day");
 delay (30000);
} else{
 Serial.println("Night");
 delay (30000);
}
 }
#This gives a set of data of whether it is night or day with a timestamp. An interval may be set under delay to tell the system when to check the amount of light. In this example we have it every 30000 ms, or every 30 seconds. 
```

Raw Data from Test Run
```{r}
#20 minute run while every 30 seconds data was collected. Light was switched every minute and a half to show it can read both light and dark. An LED would turn on in the dark room. 

DaylightDetection <-matrix(c("14:38:52.285","954","Day","14:39:22.320","961","Day","14:39:52.359","957","Day","14:40:22.380","1020","Night","14:40:52.443","1020","Night","14:41:22.461","1019","Night","14:41:52.501","954","Day","14:42:22.541","957","Day","14:42:52.548","946","Day","14:43:22.586","1020","Night","14:43:52.647","1020","Night","14:44:22.660","1020","Night","14:44:52.701","965","Day","14:45:22.742","961","Day","14:45:52.749","963","Day","14:46:22.785","1019","Night","14:46:52.817","1020","Night","14:47:22.856","1020","Night","14:47:52.891","982","Day","14:48:22.940","985","Day","14:48:52.958","959","Day","14:49:23.016","1020","Night","14:49:53.045","1020","Night","14:50:23.071","1020","Night","14:50:53.113","1012","Night","14:51:23.152","989","Day","14:51:53.172","954","Day","14:52:23.205","956","Day","14:52:53.246","1020","Night","14:53:23.249","1019","Night","14:53:53.286","1020","Night","14:54:23.337","983","Day","14:54:53.368","941","Day","14:55:23.393","941","Day","14:55:53.446","1020","Night","14:56:23.470","1020","Night","14:56:53.518","1020","Night","14:57:23.545","966","Day","14:57:53.585","960","Day","14:58:23.606","943","Day"),ncol=3,byrow=TRUE)
colnames(DaylightDetection) <- c("Time","Voltage Value","Indicates Dark or Light")
DaylightDetection <- as.table(DaylightDetection)
DaylightDetection
```
This data would be what is output by the program.

Abi's Resources
```{r}
#resources

resources <- matrix(c("https://www.elegoo.com/download/","https://startingelectronics.org/tutorials/arduino/modules/photo-resistor/","https://www.r-bloggers.com/timing-in-r/","https://www.cyclismo.org/tutorial/R/tables.html","TA0010 Arduino Uno Projects.pdf","https://www.youtube.com/watch?v=AuiWwJZQEec","file:///Users/Abi/Downloads/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf","https://www.arduino.cc/reference/en/language/structure/control-structure/if/","https://www.arduino.cc/en/Tutorial/BlinkWithoutDelay","https://www.norwegiancreations.com/2017/09/arduino-tutorial-using-millis-instead-of-delay/","https://forum.arduino.cc/index.php?topic=98735.0","https://forum.arduino.cc/index.php?topic=323164.0"),ncol=1,byrow=TRUE)
colnames(resources) <- c("Source")
rownames(resources) <- c("Photoresistor Code:","More on Photoresistors:","Timing Coding:","Table Code:","Arduino Resource:","Arduino Stop Code Tutorial","DFrobot Code Book Resource", "Arduino IF statements","Blink Without Delay for TIME","More Help on Timing Using Millis Fxn","Time Elapsed Code","More on Finding Timestamp")
resources <- as.table(resources)
resources
```
Smiley Face for Fun :)