---
title: "ComputingTwoProject"
author: "Abigail McPheeters"
date: "4/16/2020"
output: html_document
---




Abi's Section

My goal is to use a light sensor from the Beginner Kit for Arduino to record light and the time that elapses when there is light versus no light. This was to be used in a greenhuose to measure the amount of light in a day to compare with temperature to see if there is a correlation with plant growth. However, the code is all I am able to work with in the current COVID-19 quarantine. The Arduino code is shown in the following chunk. 

The set up for the Arduino is seen on page 82 in the linked PDF:https://github.com/DFRobot/Beginner-Kit-for-Arduino/raw/master/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf. A picture of the physical setup will be in the recorded video. The base code is from the same document, although tweaks have been made to record time and set a delay between reading instead of a constant stream of data. This will allow for readings to be taken at set times per day. The time set is placed in milliseconds. 

```{Uno}
#light sensor code that runs on an Arduino
#this code does not run on Rstudio, but it runs on an Arduino Uno system
// /light sensor with LED to show when the change is registered
int LED = 13; //define LED digital pin 13
int val = 0; //define the voltage value of photo diode in digital pin 0
unsigned long timeLOW = 0; //will store last time LED was updated
void setup(){
 pinMode(LED,OUTPUT); // Configure LED as output mode
 Serial.begin(9600); //Configure baud rate 9600
}
void loop(){
 val = analogRead(0); // Read voltage value ranging from 0 -1023
 Serial.println(val); // read voltage value from serial monitor
 if(val<1000){ // If lower than 1000, turn off LED
 digitalWrite(LED,LOW);
 }else{ // Otherwise turn on LED
 digitalWrite(LED,HIGH);
}
 delay(10); // delay for 10ms;
 if (val<1000 == true){   //record time when daylight presence is detected
 timeLOW = millis();
 Serial.println("Day");
 delay (30000);
} else{
 Serial.println("Night");
 delay (30000);
}
 }
#This gives a set of data of whether it is night or day with a timestamp. An interval may be set under delay to tell the system when to check the amount of light. In this example we have it every 30000 ms, or every 30 seconds. 
```

Data from Test Run
```{r}
#20 minute run where data was collected every 30 seconds. Light was switched every minute and a half to show it can read both light and dark. An LED would turn on in the dark room. 

DaylightDetection <-matrix(c("14:38:52.285","954","Day","14:39:22.320","961","Day","14:39:52.359","957","Day","14:40:22.380","1020","Night","14:40:52.443","1020","Night","14:41:22.461","1019","Night","14:41:52.501","954","Day","14:42:22.541","957","Day","14:42:52.548","946","Day","14:43:22.586","1020","Night","14:43:52.647","1020","Night","14:44:22.660","1020","Night","14:44:52.701","965","Day","14:45:22.742","961","Day","14:45:52.749","963","Day","14:46:22.785","1019","Night","14:46:52.817","1020","Night","14:47:22.856","1020","Night","14:47:52.891","982","Day","14:48:22.940","985","Day","14:48:52.958","959","Day","14:49:23.016","1020","Night","14:49:53.045","1020","Night","14:50:23.071","1020","Night","14:50:53.113","1012","Night","14:51:23.152","989","Day","14:51:53.172","954","Day","14:52:23.205","956","Day","14:52:53.246","1020","Night","14:53:23.249","1019","Night","14:53:53.286","1020","Night","14:54:23.337","983","Day","14:54:53.368","941","Day","14:55:23.393","941","Day","14:55:53.446","1020","Night","14:56:23.470","1020","Night","14:56:53.518","1020","Night","14:57:23.545","966","Day","14:57:53.585","960","Day","14:58:23.606","943","Day"),ncol=3,byrow=TRUE)
colnames(DaylightDetection) <- c("Time","Voltage Value","Indicates Dark or Light")
DaylightDetection <- as.table(DaylightDetection)
DaylightDetection
```
The table shows the out put of the data. For a real test, the daylight will be measured every few minutes (perhaps every 20 minutes). It will measure the data of daylight over the growing time of the plants. The "millis" code can run for 50 days without being reset. 

Abi's Resources
```{r}
#resources

resources <- matrix(c("https://www.elegoo.com/download/","https://startingelectronics.org/tutorials/arduino/modules/photo-resistor/","https://www.r-bloggers.com/timing-in-r/","https://www.cyclismo.org/tutorial/R/tables.html","TA0010 Arduino Uno Projects.pdf","https://www.youtube.com/watch?v=AuiWwJZQEec","https://github.com/DFRobot/Beginner-Kit-for-Arduino/raw/master/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf","https://www.arduino.cc/reference/en/language/structure/control-structure/if/","https://www.arduino.cc/en/Tutorial/BlinkWithoutDelay","https://www.norwegiancreations.com/2017/09/arduino-tutorial-using-millis-instead-of-delay/","https://forum.arduino.cc/index.php?topic=98735.0","https://forum.arduino.cc/index.php?topic=323164.0"),ncol=1,byrow=TRUE)
colnames(resources) <- c("Source")
rownames(resources) <- c("Photoresistor Code:","More on Photoresistors:","Timing Coding:","Table Code:","Arduino Resource:","Arduino Stop Code Tutorial","DFrobot Code Book Resource", "Arduino IF statements","Blink Without Delay for TIME","More Help on Timing Using Millis Fxn","Time Elapsed Code","More on Finding Timestamp")
resources <- as.table(resources)
resources
```


Saydi's Section

Goal: I want to gather temperature data using a temperature sensor from the ELEGOO Electronics Fun Kit.  

//Place the temperature sensor's three legs through F7 - F9 on a breadboard with the //writing facing towards you. Place one end of a jumper wire in the 5 volt (5V) pin on //the Arduino board, and loop the other end through the 1st hole in the positive power //rail of the breadboard and out again anywhere along the power rail. Place another //jumper wire on the positive power rail to G7 on the breadboard to connect it to the //left leg (anode) of the temperature sensor. Next, place one end of a jumper wire in //the ground (GND) pin on the Arduino board and loop the other end through the negative //power rail of the breadboard and out again anywhere along the negative power rail. //Place another jumper wire on the negative power rail to G9 on the breadboard to //connect it to the right leg (cathode) of the sensor. Lastly, connect a jumper wire //from the A0 pin on the Arduino board to G8 of the breadboard to connect it to the //output leg of the sensor 


//----Begin Code (copy from here)----
//Variables:
int varPin = A0; //A0 is the analog in pin
int val = 0; //This will store the current value from the sensor
int oldVal = 0; //This will store the last value from the sensor to compare.
unsigned long insertname = 0
void setup() {
 // put your setup code here, to run once:
Serial.begin(9600);
Serial.println("Serial connection established..\nTemperature logging started!");
}
void loop() {
 // put your main code here, to run repeatedly:
insertname = millis ();
val = analogRead(varPin); //Store the new value in its variable
Serial.print("Temp: ");
Serial.print(5.0 * val * 100 / 1024); 
Serial.println(" Degrees(Celsius)");
delay(30000); //Wait thirty seconds, then do it again. 
//----End Code (copy to here)----

#This code may also only be compatible with Arduino

Resources: 
https://www.auselectronicsdirect.com.au/assets/files/TA0010%20Arduino%20Uno%20Projects.pdf
>>>>>>> 10e37021ee3116b362c33eacc270a6035a3d78c1
