---
title: "ComputingTwoProject"
author: "Abigail McPheeters"
date: "4/16/2020"
output: html_document
---




Abi's Section

My goal is to use a photoresistor (from the Elegoo Electronics Fun Kit) to record light and the time that elapses when there is light versus no light. This was to be used in a greenhuose to measure the amount of light in a day to compare with heat to see if tehre was a correlation with plant growth. However, the code is all I am able to work with in the current COVID-19 quarantine. 

```{r}
#photoresistor code from www.elegoo.com 
int lightPin = 0;
int latchPin = 11;
int clockPin = 9;
int dataPin = 12;

int leds = 0;

void setup() 
{ 
  pinMode(latchPin, OUTPUT);
  pinMode(dataPin, OUTPUT);  
  pinMode(clockPin, OUTPUT);
}
void updateShiftRegister()
{
   digitalWrite(latchPin, LOW);
   shiftOut(dataPin, clockPin, LSBFIRST, leds);
   digitalWrite(latchPin, HIGH);
}
void loop() 
{
  int reading  = analogRead(lightPin);
  int numLEDSLit = reading / 57;  //1023 / 9 / 2
  if (numLEDSLit > 8) numLEDSLit = 8;
  leds = 0;   // no LEDs lit to start
  for (int i = 0; i < numLEDSLit; i++)
  {
    leds = leds + (1 << i);  // sets the i'th bit
  }
  updateShiftRegister();
}

#this code is in the works and needs to be tested with the Elegoo Photoresistor before alterations. It may only be compatible with a Raspberry Pi or Arduino set up.
#I need to test and perform more research before this code will be satisfactory.
```

Preliminary Timing Code for Photoresistor
```{r}
start_time = Sys.time()
#NEED TO DEVELOP 'dark' INTO PHOTORESISTOR CODE
Sys.sleep(dark=TRUE)
end_time = Sys.time()
```

Abi's Resources
```{r}
#resources

resources <- matrix(c("https://www.elegoo.com/download/","https://startingelectronics.org/tutorials/arduino/modules/photo-resistor/","https://www.r-bloggers.com/timing-in-r/","https://www.cyclismo.org/tutorial/R/tables.html"),ncol=1,byrow=TRUE)
colnames(resources) <- c("Source")
rownames(resources) <- c("Photoresistor Code:","More on Photoresistors:","Timing Coding:","Table Code:")
resources <- as.table(resources)
resources
```

Saydi's Section

Goal: I want to gather temperature data using a temperature sensor from the ELEGOO Electronics Fun Kit.  

//Place the temperature sensor's three legs through F7 - F9 on a breadboard with the //writing facing towards you. Place one end of a jumper wire in the 5 volt (5V) pin on //the Arduino board, and loop the other end through the 1st hole in the positive power //rail of the breadboard and out again anywhere along the power rail. Place another //jumper wire on the positive power rail to G7 on the breadboard to connect it to the //left leg (anode) of the temperature sensor. Next, place one end of a jumper wire in //the ground (GND) pin on the Arduino board and loop the other end through the negative //power rail of the breadboard and out again anywhere along the negative power rail. //Place another jumper wire on the negative power rail to G9 on the breadboard to //connect it to the right leg (cathode) of the sensor. Lastly, connect a jumper wire //from the A0 pin on the Arduino board to G8 of the breadboard to connect it to the //output leg of the sensor 


//----Begin Code (copy from here)----
//Variables:
int varPin = A0; //A0 is the analog in pin
int val = 0; //This will store the current value from the sensor
int oldVal = 0; //This will store the last value from the sensor to compare.
unsigned long insertname = 0
void setup() {
 // put your setup code here, to run once:
Serial.begin(9600);
Serial.println("Serial connection established..\nTemperature logging started!");
}
void loop() {
 // put your main code here, to run repeatedly:
oldVal = val; //Store the last value in the variable
val = analogRead(varPin); //Store the new value in its variable
if (oldVal != val) //If the temperature has changed, tell us the new temp
{
Serial.print("Temp: ");
Serial.print(5.0 * val * 100 / 1024); //please see note at bottom regarding this formula.
Serial.println(" Degrees(Celsius)");
}
delay(500); //Wait half a second, then do it again. (This allows the line to settle between reads.
Not really required, but it does remove a bit of jitter
}
insertname = millis ();
delay(30000);
//----End Code (copy to here)----

#This code may also only be compatible with Arduino

Resources: 
https://www.auselectronicsdirect.com.au/assets/files/TA0010%20Arduino%20Uno%20Projects.pdf
