---
title: "ComputingTwoProject"
author: "Abigail McPheeters"
date: "4/16/2020"
output: html_document
---




Abi's Section

My goal is to use an ambient light sensor from the Beginner Kit for Arduino to record light and the time that elapses when there is light versus no light. This was to be used in a greenhouse to measure the amount of light in a day to compare with temperature to see if there is a correlation with plant growth. However, no true data was collected due to the COVID-19 quarantine. The setup and code was able to be performed and a test run was performed and recorded. The Arduino code is shown in the first chunk. 

The set up for the Arduino is seen on page 82 in the linked PDF:https://github.com/DFRobot/Beginner-Kit-for-Arduino/raw/master/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf. A Prototyping Shield for Arduino from DFRobot was added to the DFRduino Uno R3. A M/M cable was connected from the Ground box to the E9 box. The negative end of the LED was connected at the E10 box with the positive end at the F10 box. A 220 resistor was added at the D7 and D4 boxes with the brown stripe at the D7 and red stripe at the D4. Another M/M cable was connected from the Green 13 box to the F3 box. Another M/M cable was connected from the Red 4 box to the L8 position. The negative end of the Ambient Light Sensor was connected at the L7 box with the positive end at the M7 box. A 10K resistor was connected from the M8 to P8 boxes with the brown/red end at M and the black/brown end at P8. A M/M cable was placed from Blue 1 to M9. Finally the last cable was connected from the P7 box to the 5V input. 
=======

The base code is from the same document in the paragraph above, although tweaks have been made to record time and set a delay between reading instead of a constant stream of data. This will allow for readings to be taken at set times per day. The time set is placed in milliseconds. 

```{Uno}
#light sensor code that runs on an Arduino
#this code does not run on Rstudio, but it runs on an Arduino Uno system
// /light sensor with LED to show when the change is registered
int LED = 13; //define LED digital pin 13
int val = 0; //define the voltage value of photo diode in digital pin 0
unsigned long timeLOW = 0; //will store last time LED was updated
void setup(){
 pinMode(LED,OUTPUT); // Configure LED as output mode
 Serial.begin(9600); //Configure baud rate 9600
}
void loop(){
 val = analogRead(0); // Read voltage value ranging from 0 -1023
 Serial.println(val); // read voltage value from serial monitor
 if(val<1000){ // If lower than 1000, turn off LED
 digitalWrite(LED,LOW);
 }else{ // Otherwise turn on LED
 digitalWrite(LED,HIGH);
}
 delay(10); // delay for 10ms;
 if (val<1000 == true){   //record time when daylight presence is detected
 timeLOW = millis();
 Serial.println("Day");
 delay (30000);
} else{
 Serial.println("Night");
 delay (30000);
}
 }
#This gives a set of data of whether it is night or day with a timestamp. An interval may be set under delay to tell the system when to check the amount of light. In this example we have it every 30000 ms, or every 30 seconds. 
```

Data from Test Run
```{r}
#20 minute run where data was collected every 30 seconds. Light was switched every minute and a half to show it can read both light and dark. A LED would turn on in the dark room. 

DaylightDetection <-matrix(c("14:38:52.285","954","Day","14:39:22.320","961","Day","14:39:52.359","957","Day","14:40:22.380","1020","Night","14:40:52.443","1020","Night","14:41:22.461","1019","Night","14:41:52.501","954","Day","14:42:22.541","957","Day","14:42:52.548","946","Day","14:43:22.586","1020","Night","14:43:52.647","1020","Night","14:44:22.660","1020","Night","14:44:52.701","965","Day","14:45:22.742","961","Day","14:45:52.749","963","Day","14:46:22.785","1019","Night","14:46:52.817","1020","Night","14:47:22.856","1020","Night","14:47:52.891","982","Day","14:48:22.940","985","Day","14:48:52.958","959","Day","14:49:23.016","1020","Night","14:49:53.045","1020","Night","14:50:23.071","1020","Night","14:50:53.113","1012","Night","14:51:23.152","989","Day","14:51:53.172","954","Day","14:52:23.205","956","Day","14:52:53.246","1020","Night","14:53:23.249","1019","Night","14:53:53.286","1020","Night","14:54:23.337","983","Day","14:54:53.368","941","Day","14:55:23.393","941","Day","14:55:53.446","1020","Night","14:56:23.470","1020","Night","14:56:53.518","1020","Night","14:57:23.545","966","Day","14:57:53.585","960","Day","14:58:23.606","943","Day"),ncol=3,byrow=TRUE)
colnames(DaylightDetection) <- c("Time","Voltage Value","Indicates Dark or Light")
DaylightDetection <- as.table(DaylightDetection)
DaylightDetection
```
The table shows the out put of the data. For a real test, the daylight will be measured every few minutes (perhaps every 20 minutes). It will measure the data of daylight over the growing time of the plants. The "millis" code can run for 50 days without being reset. 

Abi's Resources
```{r}
#resources for the project placed in a table for reading ease

resources <- matrix(c("https://www.elegoo.com/download/","https://startingelectronics.org/tutorials/arduino/modules/photo-resistor/","https://www.r-bloggers.com/timing-in-r/","https://www.cyclismo.org/tutorial/R/tables.html","TA0010 Arduino Uno Projects.pdf","https://www.youtube.com/watch?v=AuiWwJZQEec","https://github.com/DFRobot/Beginner-Kit-for-Arduino/raw/master/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf","https://www.arduino.cc/reference/en/language/structure/control-structure/if/","https://www.arduino.cc/en/Tutorial/BlinkWithoutDelay","https://www.norwegiancreations.com/2017/09/arduino-tutorial-using-millis-instead-of-delay/","https://forum.arduino.cc/index.php?topic=98735.0","https://forum.arduino.cc/index.php?topic=323164.0"),ncol=1,byrow=TRUE)
colnames(resources) <- c("Source")
rownames(resources) <- c("Photoresistor Code:","More on Photoresistors:","Timing Coding:","Table Code:","Arduino Resource:","Arduino Stop Code Tutorial","DFrobot Code Book Resource", "Arduino IF statements","Blink Without Delay for TIME","More Help on Timing Using Millis Fxn","Time Elapsed Code","More on Finding Timestamp")
resources <- as.table(resources)
resources
```


Saydi's Section

Goal: I want to gather temperature data using an LM35 Temperature Sensor and an Arduino Uno.   

//Setting up the sensor. Place the temperature sensor's three legs through F7 - F9 on a breadboard with the writing facing towards you. Place one end of a jumper wire in the 5 volt (5V) pin on the Arduino board, and loop the other end through the 1st hole in the positive power rail of the breadboard and out again anywhere along the power rail. Place another jumper wire on the positive power rail to G7 on the breadboard to connect it to the left leg (anode) of the temperature sensor. Next, place one end of a jumper wire in the ground (GND) pin on the Arduino board and loop the other end through the negative power rail of the breadboard and out again anywhere along the negative power rail. Place another jumper wire on the negative power rail to G9 on the breadboard to connect it to the right leg (cathode) of the sensor. Lastly, connect a jumper wire from the A0 pin on the Arduino board to G8 of the breadboard to connect it to the output leg of the sensor 

//The schematic can also be found on page 67 of https://github.com/DFRobot/Beginner-Kit-for-Arduino/raw/master/Beginner%20Kit%20for%20Arduino%20Tutorial.pdf. This schematic is for a temperature alarm, but the alarm can be left out or replaced with an LED. 


//----Begin Code (copy from here)----
//Variables:
int varPin = A0; //A0 is the analog in pin
int val = 0; //This will store the current value from the sensor
int oldVal = 0; //This will store the last value from the sensor to compare.
void setup() {
 // put your setup code here, to run once:
Serial.begin(9600);
Serial.println("Serial connection established..\nTemperature logging started!");
}
void loop() {
 // put your main code here, to run repeatedly:
val = analogRead(varPin); //Store the new value in its variable
Serial.print("Temp: ");
Serial.print(5.0 * val * 100 / 1024); 
Serial.println(" Degrees(Celsius)");
delay(30000); //Wait thirty seconds, then do it again. 
//----End Code (copy to here)----

#This is Arduino code


20 minute test run:
//I used the timestamps that my Arduino program gives me and we just ran the code for 20 minutes; it collected the temperature every thirty seconds. 
```{r}
TemperatureReadings<-matrix(c("17:41:27.481","21.48","17:41:57.461","21.00","17:42:27.476","21.48","17:42:57.498","21.48","17:43:27.537","21.48", "17:43:57.567","21.00","17:44:27.593","21.48","17:44:57.597","21.48","17:45:27.643","21.48","17:45:57.669","21.48","17:46:27.683","21.48","17:46:57.716","21.48","17:47:27.730","21.48","17:47:57.734","21.48","17:48:27.783","21.48","17:48:57.807","21.48","17:49:27.812","21.48","17:49:57.831","21.97","17:50:27.876","21.97","17:50:57.875","21.97","17:51:27.898","21.97","17:51:57.941","21.48","17:52:27.956","21.97","17:52:57.990","21.97","17:53:27.989","21.48","17:53:58.038","21.48","17:54:28.062","21.48","17:54:58.074","21.48","17:55:28.113","21.48","17:55:58.142","21.48","17:56:28.156","21.48","17:56:58.172","21.48","17:57:28.198","21.48","17:57:58.225","21.48","17:58:28.229","21.48","17:58:58.287","21.48","17:59:28.299","21.48","17:59:58.319","21.48","18:00:28.329","21.48","18:00:58.359","21.48", "18:01:28.390", "21.48"),ncol=2,byrow=TRUE)
colnames(TemperatureReadings) <- c("Time","Temperature in Celsius")
TemperatureReadings <- as.table(TemperatureReadings)
TemperatureReadings
```


Resources: 
https://www.auselectronicsdirect.com.au/assets/files/TA0010%20Arduino%20Uno%20Projects.pdf
>>>>>>> 10e37021ee3116b362c33eacc270a6035a3d78c1


Sierra's Section

Goal: I want to take the theoretical data collected by the first two sections of the project and create graphs to better display the information and run a t-test with theoretical values of the plants heights for the experiment that was intended to be conducted

```{r}
#Vectors with data collected from each sensor
reading=c(1:40)
voltage=c(954,961,957,1020,1020,1019,954,957,946,1020,1020,1020,965,961,963,1019,1020,1020,982,985,959,1020,1020,1020,1012,989,954,956,1020,1019,1020,983,941,941,1020,1020,1020,966,960,943)
temperature=c(21.48,21.00,21.48,21.48,21.48,21.00,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.97,21.97,21.97,21.97,21.48,21.97,21.97,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48,21.48)
#Scatter Plot showing the values for both readings over time
plot(reading, voltage, main="Light Readings Over Time", xlab="Reading Number", ylab="Voltage Measured")
plot(reading, temperature, main="Temperature Readings over Time", xlab="Reading Number", ylab="Temperature Measured")
#For the sake of demonstration we will randomly generate values for the observed difference in growth
lightheight <- runif(40, min = 0, max=2)
tempheight <- runif(40, min=0, max=2)
#Plant height would theoretically be measured and the differences in growth per measurement would be recorded and then plot against the values for each variable respectively
plot(lightheight,voltage, main="Height Growth and Voltage Correlation", xlab="Height Difference", ylab="Voltage Measured")
plot(tempheight,temperature, main="Height Growth and Temperature Correlation", xlab="Height Difference", ylab="Temperature Measured")
#Ttest between the groups to determine if one variable affected growth or if the measured heights are statistically the same
t.test(lightheight,tempheight)



Resources: 
  http://www.maths.usyd.edu.au/u/jchan/Rcommands.pdf
  https://www.statmethods.net/stats/ttest.html